---
title: "Quarto and Github Actions"
format: 
  dashboard:
    orientation: columns  
    nav-buttons: [github]
    github: https://github.com/josephlara/googlie_quarto

  
---

```{r}
#| echo: false
#| warning: false
#| message: false

library(tidyverse)
library(gt)
library(googlesheets4)
```

## Column Left
### Row 1: Introduction {height="30%"}

This Quarto document is really just an experimentation and learning project of mine.  I'm first going to do some setup procedures to set my Google credentials which will allow me to fetch content from a GoogleSheet.  The credentials are functional both when used on my local machine or as part of a 'Github Action'.

```{r}
#| warning: false
#| title: GoogleSheet Data Head

# set service account (loaded as secret from Github)
auth_path <- Sys.getenv("GSHEET_AUTH_JSON", 
                        unset = ".github/gsheet.json")
# authenticate
gs4_auth(path = auth_path)

# fetch GoogleSheet data
df <- read_sheet(
  ss = "https://docs.google.com/spreadsheets/d/1lIdlDMY30meMscm1Nn6uk9lzAYlPeI5AkqEnqzI7odk",
  sheet = "Sheet39")

```

### Row 2: Bargraph {height="70%"}
```{r}
#| echo: false
#| title: Graph of Fruits Sold

df |> 
  ggplot(aes(type, value, fill = type)) +
  geom_col() +
  coord_flip()

```

## Column Right

```{r}
#| echo: false
#| title: Number of Fruits Sold
# print data head
df |> 
  gt()

cat("Rendered at:", format(Sys.time(), "%Y-%m-%d %H:%M:%S %Z"))
```


